Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-09 draft.tex
a bit of cleanup

\begin{itemize}
\item General motivation: need to deal with partially specified preferences and as well partially specified voting rules
\item Focus on positional scoring rules
\item Robust decision criterion: minimax regret
\item Incremental elicitation of preferences can help mitigating the cognitive and communication costs
\item Novelty of the proposed method
\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, relation to necessary and possible winners \cite{Xia2008}
\end{itemize}

Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
In many situations, such as in group recommender systems, the goal is to find a consensus choice.

@@

In this paper we relax the traditional assumptions.
We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.

We an adaptive utility elicitation

We focus on positional scoring rules, that  are a particularly common methods used to aggregate rankings and determine  a winner.
We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information.%The score can be seen as a utility for the society.
%and often captures more information than is needed to determine the winner
We discuss  heuristics that allow us to determine queries that quickly allow to reduce minimax regret.

@@

\section{Conclusions}  \label{sec:conclusions}
%  Possible future works: manipulation, 
We have proposed the use of minimax regret as a way to determine a winner in a robust way when considering uncertainty on both the voting rule and the voters' preferences.

Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near optimal consensus choice in a limited number of steps.
%Our interactive elicitation methods are shown to be effective in simulations.

% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
%{\small
\bibliography{biblio}
\bibliographystyle{plain} 
%}

>>>>

\begin{itemize}
\item References: \cite{Cailloux2014}, \cite{Llamazares2013}, \cite{Konczak05}, \cite{Kalech2011}, \cite{Pini2009}, relation to necessary and possible winners \cite{Xia2008}
\end{itemize}

%General motivation: need to deal with partially specified preferences and as well partially specified voting rules
Aggregation of preference information is a central task in many computer systems (recommender systems, search engines, etc).
In many situations, such as in group recommender systems, the goal is to find a consensus choice.

@@

In this paper we relax the traditional assumptions.

%Robust decision criterion: minimax regret
We develop methods for computing the minimax- optimal alternative for scoring rules with partial preference information and partial information about the weights.

%Incremental elicitation of preferences can help mitigating the cognitive and communication costs
We adopt an adaptive utility elicitation framrwork

%Focus on positional scoring rules
We focus on positional scoring rules, that  are a particularly common methods used to aggregate rankings and determine  a winner.
We also address the problem of elicitation, providing incremental elicitation methods to acquire relevant preference information.%The score can be seen as a utility for the society.
%and often captures more information than is needed to determine the winner
We discuss  heuristics that allow us to determine queries that quickly allow to reduce minimax regret.

@@

\section{Conclusions}  \label{sec:conclusions}
%  Possible future works: manipulation, 
We have proposed the use of minimax regret as a way to determine a winner in a robust way when considering uncertainty on both the voting rule and the voters' preferences.
Our experimental results on randomly generated and real world data sets show that regret-based elicitation is effective and allow to find a near optimal consensus choice in a limited number of steps.

Future works include considering the effect of strategic agents, and considering probabilistic methods.
% Acknowledgements: We thank the reviewers for comments helping to improve the paper. 
%{\small
\bibliography{biblio}
\bibliographystyle{plain} 
%}
